Draft

### 2016-07-08 draft.tex
Adding notes for Q.S.M., and Photosynthesis course. Adding content index for readme file.

\title{Topological Insulators and Topological Superconductors}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    This is a draft.
}
\tableofcontents

@@

@@

    \begin{align}
        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
            (\eta_b,U_{ac}\dot{\psi}_c
    \end{align}
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.

@@

    \bibitem{DETA} Martin Braun. Differential Equations and Their
    Applications. 4ed. Springer.
    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

\title{Draft}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    This is a draft.
}
\tableofcontents

@@

    \subsection{By Mingyuan Hunag}
    Too boring.

    \subsection{By Wenkang Wong}
    \paragraph{Non-clone Theorem} We can easily see that there is no universal
    copy operators in Quantum Mechanics.

    \begin{proof}
    We proove it by contradiction. Let $U$ be the copy operator. By definition,
    we have
    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
    For any $\ket{\psi}$.
    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
    \begin{align*}
        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
    \end{align*}
    This is a contradiction.
    \end{proof}
    \begin{remark}
        We assume that the copyer is universal. This might seems to be too
        strong. However, if we assume that the copyer only
        works for certain states $\ket{\phi}$, then with the knowledge
        of these certain states, we could in principle create an exact copy
        of these states. This copy ,in the sense of another instance of the
        same object, of original state should not be considered to be an
        copied version of the original state.
    \end{remark}

@@

    \begin{align}
        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
            (\eta_b,U_{ac}\dot{\psi}_c
    \end{align}
    \subsection{Quantum Statistical Mechanics}
    \label{sec:Quantum Statistical Mechanics}
    \begin{defi}[Time Evolution Operator]
        The time evolution operator $U(t,t_0)$ is defined such that
        \begin{align}
            \label{eq:def_time_evo_op}
            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
        \end{align}
    \end{defi}
    It satisfy the relationship:
    \begin{align}
        \label{eq:def_time_evo_op 2}
        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
    \end{align}
    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
    Equations.

    \paragraph{Quantum Macrostates}
    Macrostates of the system depend on only a few the thermodynamic
    functions. We can form an ensemble of a large number $\mathcal{N}$ of
    microstates $\{\psi_\alpha\}$, corresponding too a given macrostates.
    The different microstates occur with probability $p_\alpha$.
    When wen no longer have exact knowledge of the microstate of a
    system the system is said to be in a \textit{mixed state}.
    The ensemble average of the quantum mechanical expectation
    value is given by:
    \begin{align}
        \label{eq:quantum_macrostates_ensemble_avg}
        \bar{\braket{O}} &= 
            \sum_\alpha p_\alpha \braket{\psi_\alpha|O|\psi_\alpha}
            = \sum_{\alpha,m,n} p_\alpha
                \braket{\psi_\alpha|m}\braket{m|O|n}\braket{n|\psi_\alpha}
                \nonumber\\
            &= \sum_{m,n} \braket{n|\rho|m}\braket{m|O|n}
                = \text{tr}(\rho O)
    \end{align}
    where we have introduced the density matrix:
    \begin{defi}[Density Matrix]
        The density matrix $\rho(t)$ is defined as
        \begin{align}
            \label{eq:density_matrix_def}
        \braket{n|\rho(t)|m} \equiv
        \sum_\alpha p_\alpha \braket{n|\psi_\alpha} \braket{\psi_\alpha|m}
        \end{align}
        or
        \begin{align}
            \label{eq:density_matrix_def_2}
            \rho(t) \equiv \sum_\alpha p_\alpha
                \ket{\psi_\alpha}\bra{\psi_\alpha}
        \end{align}
    \end{defi}
    Density matrix is denoted by $\rho(t)$ by analogy of the notation for
    P.D.F, since $\rho$ often represents density.

    Density matrix satisfies several good properties:
    \begin{itemize}
        \item Normalized
        \item Hermiticity
        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
    \end{itemize}
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.

@@

    \bibitem{DETA} Martin Braun. Differential Equations and Their
    Applications. 4ed. Springer.
    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
